Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex

To show such ability, we evaluat our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct. Note
that the baseline methods (V-DPM~\cite{Xiang14},
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.

\paragraph{Setup.}
We used detection bounding boxes and augment it using our method to
give viewpoint estimation. We used detection bounding boxes from two
different methods: VOC-DPM \cite{Pepik12} and R-CNN
\cite{Girshick14}. VOC-DPM is a variation of DPM that can estimate
viewpoint and is the state-of-the-art performance in viewpoint
estimation \cite{Xiang14}. The result is on Table \ref{tab:pascal12}
and precision recall curves for car using R-CNN + Ours are on Figure
\ref{fig:car_cnn_ap}.

We got significant improvement on viewpoint estimation by using our
method on top of general purpose detectors. Note that our method
estimates azimuth, elevation, in-plane rotation, focal length
estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
estimate discrete viewpoints.

Example outputs are on Figure \ref{fig:pascal12cnn}.

@@

\begin{tabular}{|c|c|c|c|c|c|c|}

@@

bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours. From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

>>>>

To show such ability, we evaluat our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.

\paragraph{Setup.}
We use detection bounding boxes provided by both object detectors and
augment it using our method to give viewpoint estimation. We use
detection bounding boxes from two different methods:
DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
variants trained on 8 viewpoint categories, since these perform best
in terms of AP. For both methods,
we use the original score for plotting precision-recall curves
(meaning that we can not improve over their AP), but
enrich the detections with additional viewpoint information provided
by our method. For DPM-VOC+VP, we fall back to the viewpoint
estimation provided by this method in case the confidence of our
method falls below a threshold. For R-CNN, we fall back to a default
viewpoint prediction ($0$ angles).

For both cases, we compare the performance of a discrete incarnation
of our method (Sect.~\ref{}) and our full model, including the
fine-tuning based on MCMC~\cite{Sect.~\ref{}}

Quantitative results are given in Tab.~\ref{tab:pascal12} in terms of
AP and AVP and in Fig.~\ref{fig:car_cnn_ap} in terms of
precision-recall plots and viewpoint confusion matrices. Example
outputs of our method applied to candidate object detections are given
in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
visualized in Fig.~\ref{}.

 More qualitative results are part of
supplemental material~\scream{}

\paragraph{Results.}
%
In Tab.~\ref{tab:pascal12}, we make mainly two observation. First, we
see that adding our method to DPM-VOC+VP consistently improves
performance in terms of AVP, for both car and bicycle, and across all
viewpoint bins. This is already the case for our discrete method: the
improvement ranges from $0.3$ for bicycle-8v to $5.8$ for car-4v. 
%
Using the R-CNN as the base detector increases AVP even more, in
particular for the bicycle class: for bicycle-4v, our discrete method
improves over the corresponding DPM-VOC+VP result by $12.6$.

The second observation is that the fine-tuning based on MCMC can
indeed improve pose estimation performance slightly, e.g., by $1.1$
for bicycle-16v and using the DPM-VOC+VP as the base detector, or by
$1.1$ for bicycle-16v when using the R-CNN as the base detector.

% We got significant improvement on viewpoint estimation by using our
% method on top of general purpose detectors. Note that our method
% estimates azimuth, elevation, in-plane rotation, focal length
% estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
% estimate discrete viewpoints.

@@

\begin{tabular}{|c||c||c||c|c||c|c|}

@@

bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 48.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 48.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
  and viewpoint confusion table on PASCAL 12 car validation set using
  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}
